Supplemental Material for ``Assessing United States county-level exposure for research on tropical cyclones and human health"

### 2019-07-28 writing/anderson_ehp_supp.tex
Work more on draft

@@

\begin{figure}[tbhp!]
\centering
\includegraphics[width=\linewidth]{othertopstorms}
\caption{Counties exposed, based on different exposure metrics, to the storms
with largest extent (as measured by the number of counties exposed based on any
metric) from each of the clusters shown in the Jaccard heatmap in the main text
(Figure 2).}
\label{fig:othertopstorms}
\end{figure}

@@

\begin{figure}[tbhp!]
\centering
\includegraphics[width=\linewidth]{averageexposureonlysupp}
\caption{Average number of storm exposure per decade in \ac{US} counties for
each exposure metric, based on years of for which data for all five exposure
metrics are available (1996\,--\,2011).} 
\label{fig:averageexposuresupp}
\end{figure}

@@

\begin{figure}[tbhp!]
\centering
\includegraphics[width=0.9\linewidth]{rainexamples}
\caption{Examples of storms where the rain exposure classification method fails
to capture full storm-related rainfall because of the distance constraint used
in that assessment metric. The red line on each map shows the track of the
storm. The color of each county in the map gives the cumulative precipitation
(in \si{\milli\metre}). The blue outline identifies the collection of counties
that were classified as ``exposed" based on our rainfall criteria (Table 1 of
main text). }
\label{fig:rainexamples}
\end{figure}

>>>>

\begin{comment}

@@

\end{comment}

\begin{figure}[tbhp!]
\centering
\includegraphics[width=0.9\linewidth]{rainexamples}
\caption{Examples of storms where some storm-related rainfall occured
         500 \si{\kilo\metre} or further from the storm's track. 
	 The red line on each map shows the track of the storm. 
	 The color of each county in the map gives the cumulative 
	 precipitation in the county from two days before to one day after
	 the storm's closest approach (in \si{\milli\metre}). The blue 
	 outline identifies the collection of counties
	 that were classified as ``exposed" based on the rainfall exposure 
	 criteria (Table 1 of main text), which includes the constraint
	 that the storm must have come within 500 \si{\kilo\metre} of the 
	 county. }
\label{fig:rainexamples}
\end{figure}

\begin{figure}[tbhp!]
\centering
\includegraphics[width=\linewidth]{othertopstorms}
\caption{Differences in the counties assessed as ``exposed'', based on different
	exposure metrics, for a sample of storms. These sample storms were 
	selected as the  storms with largest extent (as measured by the 
	number of counties exposed based on any metric) from each of the 
	clusters shown in the Jaccard heatmap in the main text (Figure 7).}
\label{fig:othertopstorms}
\end{figure}

@@

\begin{figure}[tbhp!]
\centering
\includegraphics[width=\linewidth]{averageexposureonlysupp}
\caption{Average number of storm exposures per decade in U.S. counties for each 
	exposure metric, limited analysis to years for which data on all five 
	exposures were available (1996\,--\,2011). The criteria behind each of 
	the five metrics is given in Table 1 of the main text. 	
	} 
\label{fig:averageexposuresupp}
\end{figure}

@@

### 2019-07-28 writing/ehp_discussion.tex
Work more on draft

Previous research has highlighted the range of impacts that tropical cyclones
can have in \ac{US} communities. However, studies have varied widely in how they
assess exposure to tropical cyclones for exposure, health impact, and other
impact studies, in some cases using distance to the tropical cyclone's track as
a surrogate metric of exposure to a tropical cyclone's hazards. Here we found
large differences in which counties are exposed to different hazards of
tropical cyclones and that distance is, at best, a moderate, and often a very
poor, surrogate for exposure to the specific tropical cyclone hazards of high
wind, extreme rainfall, flooding, and tornadoes. Use of distance as a surrogate
for any of these hazards could lead to exposure misclassification and, in the
case of tropical cyclone risk and impact studies, including epidemiological
studies, result in biased estimates.  Similarly, if such studies disagree on
their findings, it could result from the often poor agreement between exposure
classifications based on these different metrics, making studies that use
different metrics hard to compare or combine in meta-analyses. Our findings
highlight the importance of clarifying the potential pathway from tropical
cyclone hazards to health impacts when conducting tropical cyclone
epidemiological studies and basing exposure assessment on measurements of these
hazards. To help with this, we provide extensive tropical cyclone
hazard-related measurements for a large collection of historical Atlantic-basin
cyclones, aggregated at the county level to align with the spatial scale at
which much health-related data is collected.

>>>>

Previous research has highlighted the range of impacts that tropical cyclones
can have in \ac{US} communities. However, studies of tropical cyclone exposures
and their impacts have varied widely in how they assess exposure. Here we found
large differences in which counties are exposed to different hazards of
tropical cyclones and that distance is, at best, a moderate, and often a very
poor, surrogate for exposure to the specific tropical cyclone hazards of high
wind, extreme rainfall, flooding, and tornadoes. Use of distance as a surrogate
for any of these hazards could lead to exposure misclassification and, in the
case of tropical cyclone risk and impact studies, including epidemiological
studies, result in biased estimates.  Similarly, if such studies disagree on
their findings, it could result from the often poor agreement between exposure
classifications based on these different metrics, making studies that use
different metrics hard to compare or combine in meta-analyses. Our findings
highlight the importance of clarifying the potential pathway from tropical
cyclone hazards to health impacts when conducting tropical cyclone
epidemiological studies, and then basing exposure assessment on these hazards.
To help, we provide open-source tropical cyclone hazard-related measurements
for a large collection of historical Atlantic-basin cyclones, aggregated at the
county level to align with the spatial scale at which much health-related data
is collected.

### 2019-07-28 writing/ehp_methods.tex
Work more on draft

We estimated daily rainfall for each study county by aggregating
hourly~1/8\si{\degree} gridded reanalysis data from the \ac{NLDAS-2}
precipitation data files~\parencite{rui2013nldas}. These data integrate
satellite-based and land-based monitoring, applying a land-surface model to
create a reanalysis dataset that is spatially and temporally complete across
the continental \ac{US}~\parencite{rui2013nldas, alhamdan2014environmental}. To
aggregate to county-level, the hourly data at each grid point were summed to
create a daily rainfall total, and these grid point rainfall totals were then
averaged across all grid points within a county's~1990 \ac{US} Census
boundaries~\parencite{alhamdan2014environmental, cdcwonder}. These daily
county-level estimates were then matched temporally with storm tracks, using
the date when each storm was closest to each county. The cumulative
storm-associated rainfall was then calculated as the sum of rainfall from two
days before the storm's closest approach to a county to one day after.

>>>>

We estimated daily rainfall for each study county by aggregating
hourly~1/8\si{\degree} gridded reanalysis data from the \ac{NLDAS-2}
precipitation data files~\parencite{rui2013nldas}. These data integrate
satellite-based and land-based monitoring, applying a land-surface model to
create a reanalysis dataset that is spatially and temporally complete across
the continental \ac{US}~\parencite{rui2013nldas, alhamdan2014environmental}. To
aggregate to county-level, the hourly data at each grid point were summed to
create a daily rainfall total, and these grid point rainfall totals were then
averaged across all grid points within a county's~1990 \ac{US} Census
boundaries~\parencite{alhamdan2014environmental, cdcwonder}. These daily
county-level estimates were then matched temporally with storm tracks, using
the date when each storm was closest to each county. The cumulative
storm-associated rainfall was then calculated as the sum of rainfall from two
days before the storm's closest approach to a county to one day after, as 
storm-related rains often precede the passing of the storm's center.

### 2019-07-28 writing/ehp_results.tex
Work more on draft

For flood data, we compared flood status, based on event listings in the NOAA
Storm Events database, to streamflow measurements at \ac{US} Geological Survey
gages within nine sample counties (Figure~\ref{fig:floodcomparison}). Each
small plot in Figure~\ref{fig:floodcomparison} shows results for one of the
sample counties.  Each point represents a single tropical storm, and the
point's position along the x-axis shows the highest daily total streamflow
(cubic feet per second), summed across all identified streamgages in the
county, for a five-day window centered on the day of the storm's closest
approach to the county. The y-axis separates storms for which a flood event was
reported in NOAA's Storm Events database for the county with a start date
within the five-day window of the storm's closest approach to the county. The
color of each point gives the percent of streamflow gages in the county with a
daily streamflow that exceeded a threshold of flooding on any day during the
five-day window.

>>>>

For flood data, we compared flood status, based on event listings in the NOAA
Storm Events database, to streamflow measurements at \ac{US} Geological Survey
gages within nine sample counties (Figure~\ref{fig:floodcomparison}).
